### 2021-04-28 abstract.tex
Use \acrlong{fol} in abstract and hyphenate the acronym definition

The state-of-the-art superposition-based theorem provers for first order logic
rely on \glspl{sot} to constrain the applicability of inference rules,
which in turn shapes the ensuing search space.
The popular Knuth-Bendix simplification ordering is parameterized by 
\emph{symbol precedence}---a permutation of the predicate and function symbols
of the input problem's signature.
Thus, the choice of precedence has an indirect yet often substantial impact
on the amount of work required to complete a proof search successfully.

>>>>

The state-of-the-art superposition-based theorem provers for \acrlong{fol}
rely on \glspl{sot} to constrain the applicability of inference rules,
which in turn shapes the ensuing search space.
The popular Knuth-Bendix simplification ordering is parameterized by 
\emph{symbol precedence}---a permutation of the predicate and function symbols
of the input problem's signature.
Thus, the choice of precedence has an indirect yet often substantial impact
on the amount of work required to complete a proof search successfully.
